Local to global N input modelling

### 2025-06-20 07_species_layers.qmd
Tidying scripts

---
title: "07_species_layers"
format: html
editor: source
---

```{r}
library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(here)
library(terra)
library(sf)
library(qs)
library(ggplot2)
library(countrycode)
library(terra)
library(tidyterra)
library(cowplot)
library(furrr)
library(rnaturalearth)
library(aquamapsdata) # https://raquamaps.github.io/aquamapsdata/articles/intro.html
library(worrms)
library(grid)

@@

In this very crude and liberal estimation, the maximum exposure of any species to farm nutrient inputs was `r round(max(vuln_am_keys$overlap_percent), 2)`%.

>>>>

---
title: "07_species_layers"
editor: source
---

```{r setup}
#| include: false

library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(here)
library(terra)
library(sf)
library(qs)
library(ggplot2)
library(countrycode)
library(terra)
library(tidyterra)
library(cowplot)
library(furrr)
library(rnaturalearth)
library(aquamapsdata) # https://raquamaps.github.io/aquamapsdata/articles/intro.html
library(worrms)
library(grid)

@@

In this very crude and liberal estimation, the maximum exposure of any species to farm nutrient inputs was ~1.9%.

### 2025-06-20 manuscript.qmd
Tidying scripts

format: 
  html:
    theme: simplex
    css: ["extra.css"]
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 250px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em

>>>>

format: 
  html:
    theme: simplex
    css: "extra.css"
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 250px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em
